\documentclass[11pt,a4paper]{article}

%% \usepackage[T1]{fontenc} % not required if OT1 is available
%% \usepackage{helvet}      % not sure
%% \usepackage{tgadventor}         % headings
\usepackage{lmodern}            % main text
%% \usepackage{inconsolata}        % monospace
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{sectsty}
\usepackage[usenames,dvipsnames]{color}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
%% \usepackage{parcolumns}         % not sure
\usepackage{multicol}
\usepackage{tabularx}
\usepackage{amssymb}
\usepackage{tikz}

\usepackage{style}

%\allsectionsfont{\fontfamily{tgadventor}}

%\newenvironment{itemize*}%
%{\begin{itemize}%
%	\setlength{\itemsep}{1pt}%
%\setlength{\parskip}{0pt}%
%	\setlength{\itemindent}{0em}%
%\end{itemize}}
% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
%\usepackage[T1]{fontenc}
%\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{\fontfamily{phv}\selectfont{Alexander Solovets}}
\markright{\name}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = dark-gray,
  pdfauthor = {\name},
  pdfkeywords = {math, mathematic, CS, software engineer, speech recognition},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\begin{document}

\color{dark-gray}
\sf

\begin{center}
  {\Huge \bfseries \name}\\\vskip 1ex
  %%\begin{tikzpicture}[]
  %%  \draw[] plot[domain=-1.5*pi:-pi/4,samples=1000,xscale=.5,smooth] function { sin(4*x) / x };
  %%  \draw[] plot[domain=-1.5*pi:-pi/4,samples=1000,xscale=.5,smooth] function { sin(4*x) * cos(x) / x } node[right]
  %%  plot[] function {x};
  %%\end{tikzpicture}

  \newcommand{\email}{asolovets+cv@gmail.com}
  \fontfamily{qag}\selectfont{Software Engineer in Speech Processing,
  \href{mailto:\email}{\email}}
\end{center}

\small

\section{Employment}
\begin{multicols}{2}
  \raggedcolumns

  \begin{project1}{Facebook Inc.}{Menlo Park (CA), 2015 -- Present}
    \begin{items}
    \item Integrated confusion network generation into Facebook video
      captioning service to provide world alternatives in the editor.
    \item Added ARPA language model support into\\Facebook/Wit.ai speech
      recognition service.
    \item Implemented a thread-safe flyweight pattern in the acoustic model
      code, so that one model could be shared among many decoders.
    \item Created a grammar-based (thrax) solution for inverse text
      normalization problem to provide speech-to-text output in human-readable
      form.
    \item Fixed bug in acoustic modeling code, reducing the WER by 0.1\%.
    \item Developed and applied a set of automatic tools to migrate a large
      20-year-old code base in C to C\texttt{++}11.
    \end{items}
  \end{project1}

  \columnbreak

  \begin{project1}{Wit.ai Inc.}{Palo Alto (CA)/Remote, 2014 -- 2015}
    \begin{items}
    \item Designed and partially implemented an internal speech recognition
      service as the on-site\\alternative to Google's API.
    \item Trained an adapted GMM model for embedded speech recognition,
      dropping WER by 5\%.
    \end{items}
  \end{project1}

  \begin{project1}{Alpha Cephei Inc.}{Remote, 2013 -- 2014}
    \begin{items}
      \item Implemented multipass speech aligner capable of aligning long
        audios such as books and\\podcasts.
      \item Added support of acoustic model in Kaldi\\format into Sphinx4
        speech recognition library. Kaldi model supports variable
        dimension\\gaussian mixture models which allows it to keep word error
        rate at 2.5$\%$ for a particular model.
      %\item Designed and implemented a simplified API for Sphinx4 core which
      %  allowed to skip XML configuration step and setup speech recognition
      %  with just a few method calls.
    \end{items}
  \end{project1}

\end{multicols}

\section{Projects}
\begin{multicols}{2}
  \raggedcolumns

  \begin{project2}{CMU Sphinx}{\begin{tabular}{@{}l|l}Speech recognition library & C, Python\\\end{tabular}}
    \begin{items}
    \item Refactored pocketsphinx build for Android and developed it into
      standalone library that can be used in Android applications for offline
      speech recognition.
    \item Provided pocketsphinx bindings for Java and Python using SWIG:
      designed interfaces and\\implemented routines for data type conversion.
    \end{items}
  \end{project2}

  \begin{project2}{Kaldi}{\begin{tabular}{@{}l|l}Speech recognition framework & C\texttt{++}, Bash\\\end{tabular}}
    \begin{items}
    \item Fixed minor issues in data preparation scripts.
    \item Added safe-checks for model training scripts.
    \item Improved user documentation.
    \end{items}
  \end{project2}

  \columnbreak

  \begin{project2}{Review Board}{\begin{tabular}{@{}l|l}Google Summer of Code'11 & Python\\\end{tabular}}
    Command-line interface for the code review system.
    \begin{items}
    \item Designed and partially implemented a code\\generator for making
      remote API requests.
    \item Covered new and legacy code with tests\\increasing coverage from
      31$\%$ to 42$\%$.
    \end{items}
  \end{project2}

  \begin{project2}{Freedroid RPG}{\begin{tabular}{@{}l|l}Google Summer of Code'10 & C\\\end{tabular}}
    Single person role-played game.
    \begin{items}
    \item Implemented an algorithm to generate natural-looking forest maps
      based on fractals and self-similarity.
    \end{items}
  \end{project2}

\end{multicols}

%%\section{Skills}
%%\begin{multicols}{2}
%%  \raggedcolumns
%%  \begin{items}
%%  \item \textbf{CS fundamentals}: general knowledge of algorithms and
%%    data structures, understanding of x86 architecture basics,
%%    object-oriented programming, functional programming.
%%
%%    \columnbreak
%%
%%  \item \textbf{Programming languages}: C, %% C\texttt{++},
%%    Java, Python.
%%  \item \textbf{Math}: automatic speech recognition, digital signal processing,
%%    linear algebra, discrete math, statistics.
%%  \end{items}
%%\end{multicols}

\section{Education}
\begin{multicols}{2}
  \raggedcolumns
  \begin{items}
  \item \textbf{M.S. in Computer Science and Math}\\
    Far Eastern Federal University of Russia\\
    2006 -- 2011
  \end{items}
  \columnbreak
  % this hack prevents above block from breaking onto two columns
  \hspace{10mm}
\end{multicols}

%% \section{Awards}
%% \begin{items}
%%   \begin{multicols}{2}
%%     \raggedcolumns
%%   \item \textbf{\Rmnum{3} degree diploma}\\ACM ICPC'2010 NEERC (Siberian group).
%%   \item \textbf{\Rmnum{3} degree diploma}\\ACM ICPC'2009 NEERC (Siberian group).
%%     \columnbreak
%%   \item \textbf{\Rmnum{1} degree diploma}\\Game Development Contest,\\Far Eastern Federal University, 2006.
%%   \end{multicols}
%% \end{items}

\end{document}
